Validating Cell Tower Clustering for Mobility Prediction

### 2012-12-12 docs/paper589.tex
typo

In this project, we address one of the challenges faced in mobility prediction using GSM cell tower connection logs. In our context, mobility prediction in cellular
towers can be defined as the ability to predict a user's physical movement by examning the history of cell tower connections. This is very important
for mobile network operators, as several network optimizations are possible if they can forecast with reasonable accuracy
where a user will be in the future \cite{LeapGraph} \cite{Liu97anoptimal}. By being able to pre-allocate resources to towers that are most likely to
be connected to by the user, network operators can improve latency and uptime. This is increasingly important as the amount of data in cellular networks
increases: indeed, in 2010 the amount of data traffic surpassed voice traffic for the first time, and it is expected to double annually in the near future
\cite{EricssonData}.

>>>>

In this project, we address one of the challenges faced in mobility prediction using GSM cell tower connection logs. In our context, mobility prediction in cellular
towers can be defined as the ability to predict a user's physical movement by examining the history of cell tower connections. This is very important
for mobile network operators, as several network optimizations are possible if they can forecast with reasonable accuracy
where a user will be in the future \cite{LeapGraph} \cite{Liu97anoptimal}. By being able to pre-allocate resources to towers that are most likely to
be connected to by the user, network operators can improve latency and uptime. This is increasingly important as the amount of data in cellular networks
increases: indeed, in 2010 the amount of data traffic surpassed voice traffic for the first time, and it is expected to double annually in the near future
\cite{EricssonData}.
